Deliminative verbal reduplication in Mandarin Chinese

### 2024-08-25 chapters/ch02-Phenomenon.tex
Update 2024-08-25-22:21:22

\ex[]{ \gll {[[\objex{tong2xue2-men}} \objex{xu1yao4} (\objex{zai4}) \obj{tao3lun4-tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
    student-\textsc{pl} need again discuss-discuss \textsc{de} this \textsc{clf} question very important\\
    \glt `The question that the students need to discuss (again) is very important.'}
\z\z
This claim can be falsified by (\ref{ex:rel-ccl}) found in CCL.
We thus consider the contrast in (\ref{ex:rel-suihu}) a matter of providing a proper context.
\ea\label{ex:rel-ccl}
\gll \objex{er2qie3} \objex{yan3-qian2} \objex{zhe4} \objex{[[ku3-liu2} \objex{ta1} \objex{zai4} \obj{tan2-tan} \objex{de]} \objex{ren2]} \ldots\\
moreover eye-in.front.of this hard-make.stay she again discuss-discuss \textsc{de} person\\
\glt `Moreover, this person in front of her who is trying hard to make her stay to discuss a bit more \ldots'
\\\jambox{(CCL)}
\z

>>>>

\ex[]{ \gll {[[\objex{tong2xue2-men}} \objex{xu1yao4} (\objex{zai4}) \obj{tao3lun4-tao3lun4} \objex{de]} \objex{zhe4} \objex{ge4} \objex{wen4ti2]} \objex{fei1chang2} \objex{zhong4yao4}.\\
    student-\textsc{pl} need again discuss-discuss \textsc{de} this \textsc{clf} question very important\\
    \glt `The question that the students need to discuss (again) is very important.'}
\z\z
This claim can be falsified by (\ref{ex:rel-ccl}) found in CCL.
We thus consider the contrast in (\ref{ex:rel-suihu}) a matter of providing a proper context.
\ea\label{ex:rel-ccl}
\gll \objex{er2qie3} \objex{yan3-qian2} \objex{zhe4} \objex{[[ku3-liu2} \objex{ta1} \objex{zai4} \obj{tan2-tan} \objex{de]} \objex{ren2]} \ldots\\
moreover eye-in.front.of this hard-make.stay she again discuss-discuss \textsc{de} person\\\jambox{(CCL)}
\glt `Moreover, this person in front of her who is trying hard to make her stay to discuss a bit more \ldots'
\z
